\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphics}
\usepackage[singlelinecheck=off]{caption}
\usepackage{subfig}
\captionsetup[table]{aboveskip=0pt}
%\captionsetup[table]{belowskip=10pt}
\usepackage{authblk} % new

\begin{document}
\title{PHENIX Analysis Note: Identified Charged Hadron Spectra In Additional Centrality Classes in Run8 d+Au}
%\author{R. Belmont, A. Sickles}
\author[1]{R. Belmont}
\author[2]{A. Sickles}
\affil[1]{University of Michigan}
\affil[2]{Brookhaven National Laboratory}
\maketitle


\begin{abstract}
This short analysis note is a supplement to AN1018 in support of the $\left<p_T\right>$
analysis.
\end{abstract}

\newpage

\tableofcontents

\newpage


\section{Introduction}

Given the strong interest in possible signature of hydrodynamical flow in d+Au
collisions at RHIC, $\left<p_T\right>$ as a function of centrality is an important
measurement in support of these studies.  This analysis note does not discuss
the specifics of $\left<p_T\right>$ analysis itself.  Rather, we simply extend
the identified charged hadron analysis presented in AN1018 and published in PPG146
to include more centrality bins.

\section{Double interactions in the most central bins}

As discussed in AN1087 and PPG160, the Run8 data, especially the later runs,
have a very small amount of in-time pile up and a somewhat more significant
amount of out-of-time pileup.  For the 0--20\% bin, the upper limit of
contamination is 7.6\% and can likely be ignored.  For the 0--5\% bin,
the upper limit is 13.5\%, which is large enough to justify a quantitative
check on how the spectral shapes are modified.

In this analysis, we compare the spectral shapes by taking the ratio of the
raw, uncorrected spectra in high luminosity to low luminosity runs.  We divide
the runs into four luminosity categories based on the BBCLL1(no vertex) rate.
A simple, direct comparison between any two of the four categories is not
always feasible.
A comparison of uncorrected spectra between magnetic fields is an inept
comparison due to the very large differences in acceptance.
In Table~\ref{lumicat} we show the BBCLL1(no vertex) rate ranges and the
event numbers for each luminosity category.

\begin{table}[ht]
\caption{Luminosity categories}
\begin{tabular}{rrrr}
\hline
Luminosity category & BBCLL1(no vertex) rate & No. of $++$ field events & No. of $--$ field events  \\
A &    0--50 kHz & 449,986,638 &           0 \\
B &  50--100 kHz & 471,459,131 &  59,744,470 \\
C & 100--200 kHz & 428,340,263 & 291,129,781 \\
D &   $>$200 kHz &  27,399,373 & 118,645,423 \\
\hline
\end{tabular}
\label{lumicat}
\end{table}




\section{Centrality categories}

In every PHENIX d+Au analysis prior to PPG152, the centrality
was divided into four categories plus MinBias.
For Run8 the centrality definition and categorization
is discussed in AN900.
With PPG152 as an impetus, the possibility of additional
centrality categories was explored and is documented
in AN1087.
In Table~\ref{Cent4}
we present the Glauber values and bias factors for these categories.

\begin{table}[ht]
\caption{Standard and extended centrality categories}
  \begin{tabular}{rrrrrr}
    \hline\hline
    %Centrality & $\langle N_{part,d} \rangle$ & $\langle N_{part,Au} \rangle$ & $\langle N_{part} \rangle$ & $\left<N_{coll}\right>$ & bias factor\\
    Centrality & $\langle N_{part\rm{[d]}} \rangle$ & $\langle N_{part\rm{[Au]}} \rangle$ & $\langle N_{part} \rangle$ & $\left<N_{coll}\right>$ & bias factor\\
    \hline
    0--100\% & 1.61 $\pm$ 0.01 &  6.84 $\pm$ 0.39 &  8.46 $\pm$ 0.39 &  7.590 $\pm$ 0.427 & 0.889 $\pm$ 0.001\\
    \hline
     0--20\% & 1.95 $\pm$ 0.01 & 13.33 $\pm$ 0.82 & 15.28 $\pm$ 0.83 & 15.061 $\pm$ 1.013 & 0.941 $\pm$ 0.010 \\
    20--40\% & 1.84 $\pm$ 0.01 &  9.27 $\pm$ 0.63 & 11.11 $\pm$ 0.63 & 10.248 $\pm$ 0.704 & 1.000 $\pm$ 0.006 \\
    40--60\% & 1.65 $\pm$ 0.02 &  6.15 $\pm$ 0.43 &  7.80 $\pm$ 0.44 &  6.579 $\pm$ 0.433 & 1.034 $\pm$ 0.017 \\
    60--88\% & 1.36 $\pm$ 0.02 &  2.96 $\pm$ 0.18 &  4.32 $\pm$ 0.19 &  3.198 $\pm$ 0.193 & 1.031 $\pm$ 0.055 \\
    \hline
      0--5\% & 1.97 $\pm$ 0.02 &  15.82 $\pm$ 1.17 &  17.79 $\pm$ 1.18 &  18.115 $\pm$ 1.180 & 0.907 $\pm$ 0.010 \\
     5--10\% & 1.96 $\pm$ 0.02 &  13.62 $\pm$ 0.96 &  15.58 $\pm$ 0.97 &  15.501 $\pm$ 1.049 & 0.940 $\pm$ 0.007 \\
    10--20\% & 1.92 $\pm$ 0.02 &  12.16 $\pm$ 0.86 &  14.07 $\pm$ 0.86 &  13.397 $\pm$ 0.920 & 0.966 $\pm$ 0.008 \\
    20--30\% & 1.88 $\pm$ 0.03 &  10.04 $\pm$ 0.66 &  11.92 $\pm$ 0.67 &  11.264 $\pm$ 0.764 & 0.991 $\pm$ 0.011 \\
    30--40\% & 1.83 $\pm$ 0.04 &   8.68 $\pm$ 0.58 &  10.50 $\pm$ 0.60 &   9.348 $\pm$ 0.628 & 1.011 $\pm$ 0.015 \\
    40--50\% & 1.70 $\pm$ 0.03 &   6.99 $\pm$ 0.48 &   8.69 $\pm$ 0.49 &   7.528 $\pm$ 0.495 & 1.030 $\pm$ 0.021 \\
    50--60\% & 1.62 $\pm$ 0.03 &   5.53 $\pm$ 0.41 &   7.15 $\pm$ 0.43 &   5.779 $\pm$ 0.367 & 1.050 $\pm$ 0.033 \\
    60--70\% & 1.55 $\pm$ 0.03 &   4.15 $\pm$ 0.33 &   5.70 $\pm$ 0.37 &   4.257 $\pm$ 0.266 & 1.073 $\pm$ 0.055 \\
    70--88\% & 1.30 $\pm$ 0.03 &   2.62 $\pm$ 0.29 &   3.92 $\pm$ 0.31 &   2.638 $\pm$ 0.170 & 1.084 $\pm$ 0.108 \\
    \hline\hline
  \end{tabular}
  \label{Cent4}
\end{table}




\end{document}
